Edge sign prediction in general graphs and connection with Correlation Clustering

### 2017-07-11 gtx_related.tex
related works on spanners

@@

>>>>

more special cases are in~\autocite{specialCase14}, although it's for the minimum max stretch
$t^\star$.
\enquote{Note also that a number of particular graph classes (like interval
graphs, permutation graphs, asteroidal-triple–free graphs, strongly chordal graphs,
dually chordal graphs, and others) admit tree $t$-spanners for small values of $t$}

A tangential problem is \enquote{Light Approximate Shortest-path Trees (LASTs).  Given a set of
“sources” and a sink, a LAST is a tree of weight close to the minimum spanning tree (MST) on the
sources and the sink, such that the tree distance from any source to the sink is close to the
shortest-path distance. Khuller, Raghavachari, and Young (KRY95) defined and studied LASTs in the
offline setting and showed that one can get constant stretch with cost constant times the
MST.}\footnote{FOCS'17 \href{https://arxiv.org/abs/1611.00052}{arxiv.org/abs/1611.00052}}

@@

the subgraph $H$ is said to be an $(\alpha, \beta)$-spanner of $G$ if, for a pair of parameters
$\alpha \geq 1$, $\beta \geq 0$, and for every pair $u, v \in V$ of vertices, it holds that $d_H(u,
v) \leq \alpha\cdot d_G(u, v)+\beta$.

They have applications in computing approximately shortest
paths [9, 22, 28, 37], routing [48], distance oracles and
labeling schemes [49, 56, 36] and synchronization [7].

From 6:They also appear in biology in the process of reconstructing phylogenetic trees from
matrices, whose entries represent genetic distances among contemporary living species (H. J.
Bandelt, A. W. M. Dress, Reconstructing the Shape of a Tree from Observed Dissimilarity Data, Adv.
in Appl. Math. 7 (1986)). Robotics researchers have studied spanners under the constraints of
Euclidean geometry, where vertices of the graph are points in space, and edges are line segments
joining pairs of points (Chew), (Dobkin), $[DJ], [K], [KG], [LL]$.

studied in 1; 4; 6; 9; 15; 19; 22; 24; 26; 28; 30; 31; 37; 43; 51; 52; 57; 58

\begin{tabulary}{\textwidth}{LLLLL}
  \toprule
  work  & average stretch & edge size                              & weighted & time                                             \\
  \midrule
  46    & $4k + 1$        & $O(n^{1+\nicefrac{1}{k}})$             & no       & polynomial                                       \\
  6     & $2k +1$         & $O(n\cdot \ceil{n^{\nicefrac{1}{k}}})$ & yes      & $O\left(m(n^{1+\nicefrac{1}{k}}+n\log n)\right)$ \\
  40    & $2k-1$          & $O(n^{1+\nicefrac{1}{k}}+n)$           & no       & $O(m)$                                           \\
  Elkin & $2k-1$          & $n \cdot (1 + O(\frac{\log k}{n}))$    & no       & $O(m)$                                           \\
  \bottomrule
\end{tabulary}

% 22: E. Cohen, "Fast algorithms for constructing t-spanners and paths with stretch t," Proceedings
% of 1993 IEEE 34th Annual Foundations of Computer Science, Palo Alto, CA, 1993, pp. 648-658.  doi:
% 10.1109/SFCS.1993.366822
We construct t-spanners of size (number of edges) Õ(n 1+(2+\epsilon)/t )
(for any \epsilon > 0 and t such that t/(2+\epsilon) is integral). These spanners can be constructed
by a randomized algorithm that runs in Õ(mn (2+\epsilon)/t ) time.

% Halperin and Zwick [40].  Their deterministic algorithm, for an integer parame- ter k ≥ 1,
% computes a (2k − 1)-spanner with n 1+1/k + n edges in O(|E|) time. (Their result improved previous
% pioneering work by [46, 22].)

Describe the greedy algorithm of 6. Using (55 On Dynamic Shortest Paths Problems Liam Roditty, Uri
Zwick, 2004), it runs in $O(\alpha n^{2+\nicefrac{1}{\alpha}})$

peleg 2007 hardness results

46: Peleg, D. and Schäffer, A. A. (1989), Graph spanners. J. Graph Theory, 13: 99–116.
doi:10.1002/jgt.3190130114

study the problem on unweighted graph. Application to routing scheme (48: D. Peleg and E. Upfal, A
tradeoff between space and efficiency for routing tables. 20th ACM Symposium on the Theory of
Computing, Chicago (1988))
Special case for the complete graph weighted by the distance in a 2D plan. Existing $\sqrt{10}$
spanner for the $\ell_1$ metric (L. P. Chew, There is a planar graph almost as good as the complete
graph.  Proceedings of the 2nd ACM Symposium on Computational Geometry, (1986)) (improved to
$\sqrt{4+2\sqrt{2}}$ by N. Bonichon, C. Gavoille, N. Hanusse, L. Perkovic The stretch factor of
$\ell_1$ and $\ell_{\infty}$ Delaunay triangulations European Symposium on Algorithms (ESA) (2012))
and $\phi \pi$ for $\ell_2$ (D. P. Dobkin, S. J. Friedman, and K. J. Supowit, Delaunay graphs are
almost as good as complete graphs. 28th IEEE Symposium on the Foundations of Computer Science,
(1987)) (improved to $1.998$ by Ge Xia. 2011. Improved upper bound on the stretch factor of delaunay
triangulations. In Proceedings of the twenty-seventh annual symposium on Computational geometry
(SoCG '11)). See (Prosenjit Bose, Michiel Smid, On plane geometric spanners: A survey and open
problems, Computational Geometry, Volume 46, Issue 7, 2013) for more on the 2D case.
In undirected graph, finding a spanner with less than $k$ edges is \NPc{} (theorem 2.2)
For $k<n$, one can construct in polynomial time a $(4\log_k n +1)$ spanner with less than $kn$ edges
(theorem 2.4) giving for instance ($k=2$) $O(\log n)$ spanner with $O(n)$ edges and
($k=n^{\nicefrac{1}{r}}$, $r\geq 1$) a $(4r+1)$ spanner with $O(n^{1+\nicefrac{1}{r}})$ edges
(matching lower bound within constant factor). For every $d \geq 0$, the $d$-dimensional cube has a
$3$-spanner with fewer than $7\time 2^d$ edges (Lemma 2.10 from 47: D. Peleg and J. D. Ullman. An
optimal synchronizer for the hypercube. SIAM J. on Comput., 18:740–747, 1989)
For chordal graphs: for every $n$-vertex chordal graph there exists a $2$-spanner with
$O(n\sqrt{n})$ edges (matching lower bound), a $3$-spanner with $O(n \log n)$ edges and a $5$-spanner
with $O(n)$ edges.
Much more difficult for directed graph, according to Theorem 4.2: For every $t \geq 1$ there are
infinitely many $n$-vertex directed graphs for which every $t$-spanner requires
$\Omega(\nicefrac{n^2}{t^2})$ edges.
